\vspace{1.0cm} \huge \bf Supplemental information:\\ \LARGE Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2014-07-16 fluB_supp.tex
Enable cross-references between main and supp text.
Add 1600 genomes LD, move figures to right places.
Mention supplementary figures.
Address #29 and to some extent #13.

@@

\begin{figure}[h]
	\centering		
	\includegraphics[width=0.65\textwidth]{figures/InfB_normalizedApproxSPR.png}
	\caption{\textbf{Normalized approximate SPR distances between pairs of segments.}
Following the normalization procedure approximate SPR distances are similar across all pairwise comparisons.
We interpret this as lack of evidence for small-scale topological similarities between trees of all segments, which we expect to arise if any two segments were being co-packaged and co-reassorted.
All vertical lines indicating uncertainty are 95\% highest posterior densities (HPDs).}
	\label{SPRdistances}
\end{figure}

@@

@@

>>>>

% reference figures across documents
\usepackage{xr}
\externaldocument{fluB}

@@

\begin{figure}[h]
	\centering		
	\includegraphics[width=0.65\textwidth]{supp_figures/InfB_normalizedApproxSPR.png}
	\caption{\textbf{Normalized approximate SPR distances between pairs of segments.}
Following the normalization procedure approximate SPR distances are similar across all pairwise comparisons.
We interpret this as lack of evidence for small-scale topological similarities between trees of all segments, which we expect to arise if any two segments were being co-packaged and co-reassorted.
All vertical lines indicating uncertainty are 95\% highest posterior densities (HPDs).}
	\label{SPRdistances}
\end{figure}

@@

\begin{figure}
\centering  
\includegraphics[width=0.45\textwidth]  {supp_figures/InfB_seqCountries.452.png}
\caption{\textbf{Geographic distribution of sequences in the primary dataset.}
Sequences were assigned to the ``other'' category if there were less than 5 sequences from that country.
Most of the genomes in the primary dataset were sampled in the USA.}
\label{geoSeqs4}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.45\textwidth]  {supp_figures/InfB_seqCountries.1600.png}
\caption{\textbf{Geographic distribution of sequences in the secondary dataset.}
Sequences were assigned to the ``other'' category if there were less than 5 sequences from that country.
Most of the genomes in the secondary dataset were sampled in Australia.}
\label{geoSeqs1600}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.75\textwidth]  {supp_figures/InfB_Ntransitions.png}
\caption{\textbf{Numbers of trait transitions in each tree.}
The numbers shown are the mean inferred number of trait transitions (minus one to account for the initial Vic--Yam split) in a given tree and trait combination.
The numbers in brackets correspond to 95\% highest posterior density intervals.}
\label{Ntransitions}
\end{figure}

@@

\clearpage
